Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-06 img/bempp_overview.tex
working on bempp section

\draw[line width=1pt] (0.5,0.5) -- (0.5,0.7);
\draw[line width=1pt] (1.7,0.5) -- (1.7,0.7);
\draw[line width=1pt] (2.9,0.5) -- (2.9,0.7);
\draw[line width=1pt] (4.1,0.5) -- (4.1,0.7);
\draw[line width=1pt] (4.1,1.2) -- (4.1,1.4);

\draw[line width=1pt,line join=round,line cap=round,bemppgrey] (0,0) rectangle (4.6,0.5);
\node at (2.3,0.25) {\texttt{bempp.api}};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (0,0.7) rectangle (1,1.2);
\node at (0.5,0.95) {\footnotesize grids};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (1.2,0.7) rectangle (2.2,1.2);
\node at (1.7,0.95) {\footnotesize spaces};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (2.4,0.7) rectangle (3.4,1.2);
\node at (2.9,0.95) [text width=1.45cm,align=center] {\footnotesize grid\\[-1.2mm]functions};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (3.6,0.7) rectangle (4.6,1.2);
\node at (4.1,0.95) {\footnotesize operators};
\draw[line width=1pt,line join=round,line cap=round,bemppgrey] (3.45,1.4) rectangle (4.75,1.9);
\node at (4.1,1.65) {\footnotesize\texttt{bempp.core}};

>>>>

\draw[line width=1pt] (0.35,0.5) -- (0.35,0.7);
\draw[line width=1pt] (1.3,0.5) -- (1.3,0.7);
\draw[line width=1pt] (2.65,0.5) -- (2.65,0.7);
\draw[line width=1pt] (4.1,0.5) -- (4.1,0.7);
\draw[line width=1pt] (4.1,1.2) -- (4.1,1.4);

\draw[line width=1pt,line join=round,line cap=round,bemppgrey] (0,0) rectangle (4.6,0.5);
\node at (2.3,0.25) {\pyth{bempp.api}};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (0,0.7) rectangle (0.7,1.2);
\node at (0.35,0.95) {\footnotesize \pyth{Grid}};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (0.9,0.7) rectangle (1.7,1.2);
\node at (1.3,0.95) {\footnotesize \pyth{Space}};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (1.9,0.7) rectangle (3.4,1.2);
\node at (2.65,0.95) {\footnotesize \pyth{GridFunction}};
\draw[line width=1pt,line join=round,line cap=round,bempporange] (3.6,0.7) rectangle (4.6,1.2);
\node at (4.1,0.95) {\footnotesize \pyth{Operator}};
\draw[line width=1pt,line join=round,line cap=round,bemppgrey] (3.45,1.4) rectangle (4.75,1.9);
\node at (4.1,1.65) {\footnotesize\pyth{bempp.core}};
